Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-21 talk/pepm2011/paper.tex
A typo, and a semicolon (sorry, couldn't resist).

In the snippet above, the two \lstinline{new} operations are removed and two
static objects are constructed. The \lstinline{set} operations manipulate a
static object, therefore they can be removed as well and their effect is
remembered in the static objects.

@@

Lifting a static object puts \lstinline{new} and \lstinline{set} operations into
the output trace. Those operations produce an object at runtime that has the
same shape that the static object describes. This process is a bit delicate,
because the static objects could form an arbitrary graph structure. In our
example is is simple, though:

>>>>

In the snippet above, the two \lstinline{new} operations are removed and two
static objects are constructed. The \lstinline{set} operations manipulate a
static object, therefore they can be removed as well; their effect is
remembered in the static objects.

@@

Lifting a static object puts \lstinline{new} and \lstinline{set} operations into
the output trace. Those operations produce an object at runtime that has the
same shape that the static object describes. This process is a bit delicate,
because the static objects could form an arbitrary graph structure. In our
example it is simple, though:
